---
title: "Project BellaBeat Capstone"
author: "Muhammad Hamzah Fyrzatullah"
date: "2022-09-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install and Load Package
```{r}
install.packages("tidyverse")
install.packages("skimr")
install.packages("janitor")
install.packages("sqldf")

library(tidyverse)
library(skimr)
library(janitor)
library(sqldf)
```

##upload datasets
```{r}
activity<-read.csv("dailyActivity_merged.csv")
calories<-read.csv("dailyCalories_merged.csv")
sleep_day<-read.csv("sleepDay_merged.csv")
intensities<-read.csv("dailyIntensities_merged.csv")
weight_log<-read.csv("weightLogInfo_merged.csv")
```

## For each dataframe the first six values and colnames.
```{r}
head(activity)
colnames(activity)
head(calories)
colnames(calories)
head(sleep_day)
colnames(sleep_day)
head(intensities)
colnames(intensities)
head(weight_log)
colnames(weight_log)
```

## 5 data frame have same  'ID' field
## activity,calories and intensities have similar column. use SQL to join data table
```{r}
activity2<-activity %>% select(Id,ActivityDate,Calories)
head(activity2)
sql_check1<-sqldf('select * from activity2 intersect select * from calories')
head(sql_check1)
nrow(sql_check1)
activity3<-activity %>% select(Id,ActivityDate,SedentaryMinutes,LightlyActiveMinutes,FairlyActiveMinutes,VeryActiveMinutes,SedentaryActiveDistance,LightActiveDistance,ModeratelyActiveDistance,VeryActiveDistance)
head(activity3)
sql_check2<-sqldf('select * from activity3 intersect select * from intensities')
head(sql_check2)
nrow(sql_check2)
```

## Clean Data
```{r}
n_distinct(activity$Id)
n_distinct(sleep_day$Id)
n_distinct(weight_log$Id)
```

## Number of observation
```{r}
nrow(activity)
nrow(sleep_day)
nrow(weight_log)
```

## Statistic
```{r}
activity %>% select(TotalSteps,TotalDistance,SedentaryMinutes,VeryActiveMinutes) %>% summary()
sleep_day %>% select(TotalSleepRecords,TotalMinutesAsleep,TotalTimeInBed) %>% summary()
weight_log %>% select(WeightPounds,BMI) %>% summary()
```

## visualization plot the relationship graph
```{r}
ggplot(activity,mapping = aes(x=TotalSteps,y=SedentaryMinutes,color=Calories))+geom_point()
ggplot(activity,mapping = aes(x=TotalSteps,y=Calories))+geom_point()+geom_smooth(formula = 'y~x',method = lm)
```

## #theres a large spread towards the lower amounts.let make a residuals or the differences between the observed values and the estimated value.
```{r}
calories.lm<-lm(Calories~TotalSteps,data = activity)
calories.res<-resid(calories.lm)
plot(activity$TotalSteps,calories.res,ylab="Residuals",xlab = "Total Steps",main = "Calories Burned")
abline(0,0)
```

##plot density of the residuals
```{r}
plot(density(calories.res))
```

## Checking Normality
```{r}
qqnorm(calories.res)
qqline(calories.res)
```

##sleep and time in bed
```{r}
ggplot(sleep_day,mapping = aes(x=TotalMinutesAsleep,y=TotalTimeInBed))+geom_point()
```

##combined dataset
```{r}
combined<-merge(sleep_day,activity,by="Id")
head(combined)
nrow(combined)
n_distinct(combined$Id)
```

##visualization plot the graph veryactive minutes
```{r}
ggplot(combined,mapping = aes(x=VeryActiveMinutes,y=Calories))+geom_point()+geom_smooth(formula = y~x,method = lm)
ggplot(combined,mapping = aes(x=FairlyActiveMinutes,y=Calories))+geom_point()+geom_smooth(formula = y~x,method = lm)
```

